HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
Final edits, this version is hopefully the final submitted version

{\small
\begin{tabular}{|l|l|l|l|}
\hline
L & Linker &  A & Participant \\
H & Scene & R & Relator \\
P & Process & C & Centre \\
\hline
\end{tabular}
}
    \end{center}
\caption{\label{fig:ucca_example_v2}
  Sample UCCA annotation where leaves correspond to words and nodes to units.
  The dashed edge indicates that ``Tom'' is also a participant in the ``moved to NYC''
  Scene. Edge labels mark UCCA categories, listed  in the table.}
%which are largely ignored in this work
\end{figure}

@@

@@

In Figure~\ref{fig:hume_tree_v2} we can see an example of a possible HUME
annotation, with the translation shown in English for ease of comprehension.
When evaluating ``to NYC'' the annotator looks at the translation and sees the
word ``stateside''. This word captures the whole phrase and so we mark this
non-leaf node with an atomic label. Here we choose ``Orange'' since
it approximately captures the meaning
in this context. The ability to mark non-leaves with atomic labels allows
the annotator to account for translations which only correspond at the phrase
level. Another feature highlighted in this example is that the root node is
``Adequate''. This is because the root node still has two Scenes linked by one linker and
so the relationship between child nodes is maintained. There is an error caused by a wrong
translation of the linker ``After'' which translates as ``by'' and this is
marked as ``Red'', but this error is marked at the level at which it occurs.

@@

 The child components of a structural node are marked with different coloured rectangles. When navigating through the different source sentence nodes, one can see the relevant sections of the translation because the aligned words in the translation are highlighted in the complete sentence above. Aligned translations are also shown in black alongside the source node. If the node is aligned to a set of discontiguous words in the translation, then the unaligned words that appear in between the aligned words are shown in red. Even if these words are not directly aligned to the source node, they 
will likely change the meaning of the translation and must be considered when marking 
the translation as correct or not. The alignments are meant just as a guide. The annotator should  look at the complete translation when deciding on the evaluation of a node. The translation could have content added before or after the node which changes its
 structure or meaning. If an extra component is prepended to a structural node, for example, it should be marked as ``Bad''.
}

@@

In order to assess the consistency of the annotation, we measure the Inter-Annotator
Agreement (IAA) using Cohen's Kappa on the multiply-annotated portions of the data.
For German, Polish and Romanian we used two annotators, with a significant overlap
between the sentences they annotated. For Czech we had the entire batch
annotated by one main annotator and multiple secondary annotators, 
each annotating a sub-part of the batch.

@@

There are however a number of other serious consequences on focusing on verbal
predicates. We conducted an analysis of the English UCCA Wikipedia
corpus (5324 sentences)
in order to assess the impact of the following problems: 
\\
\begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only considers non-auxiliary instances of ``be''.
\\
\item[Nominal argument structures,] which are ignored by  HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\\
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences, but ignored by HMEANT.
An example where a linker is omitted in translation in our experiments is
with the source \equo{However, this review\dots}, which was translated to
the German \equo{Diese \"Uberpr\"ufung\dots} (lit. \equo{This review}).
This omission will not be taken into account by HMEANT at all\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified non-auxiliary instances of ``be'' and nouns using the NLTK standard tagger. Nominative argument structures are here defined as Scenes whose main relation is headed by a noun.}.
\end{inparadesc}

@@

In HMEANT, there are no guidelines as to when to propagate an error. In HUME,
errors are localised as much as possible to where they occur,
by the separation of atomic and structural nodes.
This allows us to calculate more accurately the total score of the sentence.

@@

We have introduced HUME, a human semantics based MT evaluation measure which addresses
a wide range of semantic phenomena. We have shown that it can be reliably annotated in 
several languages, and that annotation quality is robust to sentence length.
We believe that HUME and a future automated version of HUME will be able to guide the
development of a more semantically aware approach to MT.

>>>>

{\small
\begin{tabular}{|l|l|l|l|}
\hline
L & Linker &  A & Participant \\
H & Scene & R & Relater \\
P & Process & C & Centre \\
\hline
\end{tabular}
}
    \end{center}
\caption{\label{fig:ucca_example_v2}
  Sample UCCA annotation where leaves correspond to words and nodes to units.
  The dashed edge indicates that ``Tom'' is also a participant in the ``moved to NYC''
  Scene. Edge labels mark UCCA categories, listed  in the table.}
%which are largely ignored in this work
\end{figure}

@@

In Figure~\ref{fig:hume_tree_v2} we can see an example of a possible HUME
annotation, with the translation shown in English for ease of comprehension.
When evaluating ``to NYC'' the annotator looks at the translation and sees the
word ``stateside''. This word captures the whole phrase and so we mark this
non-leaf node with an atomic label. Here we choose ``Orange'' since
it approximately captures the meaning
in this context. The ability to mark non-leaves with atomic labels allows
the annotator to account for translations which only correspond at the phrase
level. Another feature highlighted in this example is that by separating structural
and atomic nodes, we are able to define where an error occurs, and localise
the error to its point of origin. The linker ``After'' is translated incorrectly as ``by''
which changes the meaning of the entire sentence. This error is captured at
the atomic level, and it is labelled Red. The sentence still contains two scenes and
a linker and therefore we mark the root node as structurally correct, Adequate.

@@

@@

 The child components of a structural node are marked with different coloured rectangles. When navigating through the different source sentence nodes, one can see the relevant sections of the translation because the aligned words in the translation are highlighted in the complete sentence above. Aligned translations are also shown in black alongside the source node. If the node is aligned to a set of dis-contiguous words in the translation, then the unaligned words that appear in between the aligned words are shown in red. Even if these words are not directly aligned to the source node, they 
will likely change the meaning of the translation and must be considered when marking 
the translation as correct or not. The alignments are meant just as a guide. The annotator should  look at the complete translation when deciding on the evaluation of a node. The translation could have content added before or after the node which changes its
 structure or meaning. If an extra component is prepended to a structural node, for example, it should be marked as ``Bad''.
}

@@

In order to assess the consistency of the annotation, we measure the Inter-Annotator
Agreement (IAA) using Cohen's Kappa on the multiply-annotated portions of the data.
%For German, Polish and Romanian we used two annotators, with a significant overlap
%between the sentences they annotated. For Czech we had the entire batch
%annotated by one main annotator and multiple secondary annotators, 
%each annotating a sub-part of the batch.

@@

There are however a number of other serious consequences on focusing on verbal
predicates. We conducted an analysis of the English UCCA Wikipedia
corpus (5324 sentences)
in order to assess the impact of the following problems: 
\\
\begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only consider non-auxiliary instances of ``be''.
\\
\item[Nominal argument structures,] which are ignored by  HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\\
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences, but are ignored by HMEANT.
An example where a linker is omitted in translation in our experiments is
with the source \equo{However, this review\dots}, which was translated to
the German \equo{Diese \"Uberpr\"ufung\dots} (lit. \equo{This review}).
This omission will not be taken into account by HMEANT at all\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified non-auxiliary instances of ``be'' and nouns using the NLTK standard tagger. Nominative argument structures are here defined as Scenes whose main relation is headed by a noun.}.
\end{inparadesc}

@@

In HMEANT, an error in a child node often results in the parent node
being penalised as well. This makes it harder to quantify the true scale of  
the original error, as its effect gets propagated up the tree. 
In HUME, errors are localised as much as possible to where they occur,
by the separation of atomic and structural nodes (See Fig \ref{fig:hume_tree_v2} 
for an example).
This allows us to calculate the total score of the sentence more accurately.

@@

We have introduced HUME, a human semantics based MT evaluation measure which addresses
a wide range of semantic phenomena. We have shown that it can be efficiently and 
reliably annotated in 
several languages, and that annotation quality is robust to sentence length.
We believe that HUME, and a future automated version of HUME, will be able to guide the
development of a more semantically aware approach to MT.
